---
jupyter:
  jupytext:
    formats: ipynb,R:percent,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
      jupytext_version: 1.8.1
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# More `ggplot` Figures Peer Review

## PUT YOUR NAME HERE: Marcio Woitek

```{r setup, include=FALSE}
library(tidyverse)
library(RColorBrewer)
```

## Problem 1

Create the figure in the solution for Problem 1 using the data included in the
R Markdown file.

```{r problem_1_data, include=FALSE}
set.seed(12345)
var1 <- runif(50, 0, 10)

set.seed(12345)
var2 <- var1 + rnorm(50, 5, 2)

set.seed(12345)
var3 <- var1 * (-rnorm(50, 1, .2))

dat1 <- tibble(var1, var2, var3)
```

```{r problem_1, echo=FALSE, message=FALSE}

```

## Problem 2

Create the figure in the solution for Problem 2 using the data included in the
R Markdown file.

```{r problem_2_data, include=FALSE}
set.seed(10)
var1 <- runif(50, 0, 10)

set.seed(10)
var2 <- var1 + rnorm(50, 5, 2)

set.seed(10)
var3 <- var1 * (-rnorm(50, 1, .2))

dat2 <- tibble(var1, var2, var3)
```

```{r problem_2, echo=FALSE, message=FALSE}

```

## Problem 3

Create the figure in the solution for Problem 3 using the data included in the
R Markdown file.

```{r problem_3_data, include=FALSE}
set.seed(12)
var1 <- runif(50, 0, 10)

set.seed(12)
var2 <- var1 + rnorm(50, 5, 2)

set.seed(12)
var3 <- var1 * (-rnorm(50, 1, .2))

dat3 <- tibble(var1, var2, var3)
```

```{r problem_3, echo=FALSE}

```

## Problem 4

Create the figure in the solution for Problem 4 using the data included in the
R Markdown file.

```{r problem_4_data, include=FALSE}
set.seed(5678)
var1 <- rnorm(10, 25, 5)

names <- letters[1:10]

dat4 <- tibble(names, var1)
```

```{r problem_4, echo=FALSE}

```

## Problem 5

Create the figure in the solution for Problem 5 using the data included in the
R Markdown file.

```{r problem_5_data, include=FALSE}
set.seed(13)
var1 <- rnorm(10, 25, 5)

names <- letters[1:10]

dat5 <- tibble(names, var1)
```

```{r problem_5, echo=FALSE}

```

## Problem 6

Create the figure in the solution for Problem 6 using the data included in the
R Markdown file.

```{r problem_6_data, include=FALSE}
set.seed(8)
fiction <- tibble(
    Genre = rep("Fiction", 5),
    Time = seq(1:5),
    Total = sample(1:10, 5)
)

set.seed(7)
biography <- tibble(
    Genre = rep("Biography", 5),
    Time = seq(1:5),
    Total = sample(1:10, 5)
)

set.seed(9)
mystery <- tibble(
    Genre = rep("Mystery", 5),
    Time = seq(1:5),
    Total = sample(1:10, 5)
)

books_checked_out <- bind_rows(fiction, biography, mystery)
```

```{r problem_6, echo=FALSE}

```

## Problem 7

Create the figure in the solution for Problem 7 using the data included in the
R Markdown file.

```{r problem_7_data, include=FALSE}
books_checked_out2 <- books_checked_out %>%
    filter(Time == 1 | Time == 5) %>%
    pivot_wider(names_from = Time, values_from = Total) %>%
    rename(Time1 = `1`, Time5 = `5`)
```

```{r problem_7, echo=FALSE, message=FALSE}

```

## Problem 8

Create the figure in the solution for Problem 8 using the data included in the
R Markdown file.

```{r problem_8_data, include=FALSE}
pie_dat <- c(1, 2, 3, 4, 5)
```

```{r problem_8, echo=FALSE}
my_color <- brewer.pal(5, "Spectral")
```
